\section{Conclusion}
Using the Mutual Information as an objective function, it was shown possible to optimize 
the locations of data points of a linear regression model to maximize the expected information gain from measuring at such data points.
This was shown when using the exact posterior distribution 
and shown theoretically using the variational approximation of the posterior distribution.
The latter required the use of the Implicit Function Theorem to differentiate through the nested optimization problems.
Implementing the gradient efficiently and correctly using the Implicit Function Theorem was however not possible within the time-frame of the project,
so it is yet to show the practicality of the method.

While the theoretical derivations of the method are kept simple by using a linear regression model, the implementation is still very inefficient
due to the nested optimization, even after several batching initiatives were taken.
Since the optimization relied on sampling methods, the outer optimization algorithm required stochastic optimization methods,
which usually requires a lot of iterations to converge. Thus, a lot of further trial-and-error is required to make the implementation suitable for real-world applications.
Specifically, the implementation was not tested on other types of model, where an optimal design is easier to recognize, which could lead to more confidence in the correctness of the implementation.
Another area of further research is within using parallelization to compute multiple samples of the gradient at once.
